\documentclass{article} 
\usepackage[a4paper,margin=2.5cm,right=7cm]{geometry}

\usepackage{todonotes}
\setlength{\marginparwidth}{5cm}

\begin{document}

\section{Facebook: Jane Doe}
Once upon a time,
\todo[color=red!40]{from Facebook profile}
Jane Doe,
\todo[color=green!40]{from Facebook likes}
who likes pizza and ice cream,
wondered how she was connected to the Chicago Theatre.
Many of her friends were curious
why she wanted to know that,
but of course, that didn't stop
\todo[color=red!40]{from Facebook profile}
Jane.

\section{DBpedia: David Guetta}
The thing is,
\todo[color=red!40]{from Facebook profile}
Jane really likes David Guetta.

\todo[color=green!40]{from DBpedia}
Pierre David Guetta (7 November 1967), known professionally as David Guetta, is a French house music producer and DJ. Originally a DJ at nightclubs during the 1980s and 1990s, he co-founded Gum Productions and released his first album, Just a Little More Love, in 2002.

\section{DBpedia: Paris}
\todo[color=red!40]{from DBpedia property}
The birth place of David Guetta is Paris, France.

\todo[color=green!40]{from DBpedia}
Paris is the capital and largest city of France. It is situated on the river Seine, in northern France, at the heart of the Île-de-France region (or Paris Region, French: Région parisienne)%
\footnote{We could filter out text within parentheses.}.

\section{DBpedia: Eiffel Tower}
\todo[color=red!40]{from DBpedia property}
The Eiffel Tower is located in Paris.

\todo[color=green!40]{from DBpedia}
The Eiffel Tower (nickname La dame de fer, the iron lady) is a puddle iron lattice tower located on the Champ de Mars in Paris. Built in 1889 as the entrance arch to the 1889 World's Fair, it has become both a global cultural icon of France and one of the most recognizable structures in the world. The tower is the tallest building in Paris and the most-visited paid monument in the world; millions of people ascend it every year.

\end{document}
